%-----------EXPERIENCE-----------%
\section{Positions Held}
\resumeSubHeadingListStart

    \resumeSubheading
    {Google Research}{May 2023 -- Oct 2023}
    {Student Researcher}{Cambridge, MA}
    \resumeItemListStart
        \resumeItem{Supervised by Dr. Hakan Erdogan \scholarLink{https://scholar.google.com/citations?user=Ar0No6YAAAAJ&hl=en}, Dr. John Herhsey \scholarLink{https://scholar.google.com/citations?user=ACcAdXgAAAAJ&hl=en}, and Dr. Scott Wisdom \scholarLink{https://scholar.google.com/citations?user=kJM6N7IAAAAJ&hl=en}}
        \resumeItem{Working on next-level unsupervised audio source separation problems}
    \resumeItemListEnd
    
    \resumeSubheading
    {Mitsubishi Electric Research Labs (MERL)}{Summers in 2021 - 2022}
    {Research Intern}{Cambridge, MA}
    \resumeItemListStart
        \resumeItem{Received \$15’000 of gift-money from MERL to work on the \textit{``Cocktail Fork Problem''}}
        \resumeItem{Hosted by Dr. Gordon Wichern \scholarLink{https://scholar.google.com/citations?user=JVkh89YAAAAJ&hl=en} and Dr. Jonathan Le Roux \scholarLink{https://scholar.google.com/citations?user=aUpxty8AAAAJ&hl=en}}
        \resumeItem{Derived and implemented new models and optimization methods for audio analysis with applications to source separation in challenging multi-source environments and using advanced machine learning techniques}
    \resumeItemListEnd

    \resumeSubheading
    {Signals and AI Group in Engineering (SAIGE), Indiana University}{Jan 2021 - Present}
    {Research Assistant}{Bloomington, IN}
    \resumeItemListStart
        \resumeItem{Supervised by Prof. Minje Kim \scholarLink{https://scholar.google.com/citations?user=hEfnFKAAAAAJ&hl=en}}
        \resumeItem{Conducting research pertaining to neural audio coding and audio source separation problems}
    \resumeItemListEnd

    \resumeSubheading
    {Senseable Intelligence Group, Massachusetts Institute of Technology (MIT)}{Jan 2021 - Present}
    {Technical Lab Assistant}{Cambridge, MA}
    \resumeItemListStart
        \resumeItem{Contractor for Senseable Intelligence Group, McGovern Institute for Brain Research, led by Dr. Satrajit Gosh \scholarLink{https://scholar.google.com/citations?user=QnYCqUsAAAAJ&hl=en}}
    \resumeItemListEnd

    \resumeSubheading
    {Apple Inc.}{Jun 2016 - Jul 2019}
    {Content Engineer}{Cupertino, CA}
    \resumeItemListStart
        \resumeItem{Software engineer for Apple’s pro Audio \& Music Apps (LogicPro, GarageBand) \webLink{https://www.apple.com/logic-pro/}}
        \resumeItem{Designed real-time MIDI processing systems in C++ for Apple's virtual musical instruments}
    \resumeItemListEnd

    \resumeSubheading
    {Electronic Production \& Design Dept, Berklee College of Music}{Sep 2015 - May 2016}
    {Programming Tutor}{Boston, MA}
    \resumeItemListStart
        \resumeItem{Tutored and mentored EPD students for technical classes: \textit{``Audio Programming in C'', ``Digital Signal Processing'', ``Csound'', ``Max/MSP''}}
    \resumeItemListEnd


\resumeSubHeadingListEnd